Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-06-08 Paper.tex
Explain that ecrecover only accepts v={27,28}
Update Paper.tex
Co-authored-by: Alex Beregszaszi <alex@rtfs.hu>
Explain that ecrecover only accepts v={27,28} (#860)
* Explain that ecrecover only accepts v={27,28}

* Update Paper.tex

Co-authored-by: Alex Beregszaszi <alex@rtfs.hu>

* Update Paper.tex

Co-authored-by: Andrew Ashikhmin <34320705+yperbasis@users.noreply.github.com>

Co-authored-by: Andrew Ashikhmin <34320705+yperbasis@users.noreply.github.com>
Restrictions on r & s in ECDSARECOVER precompile

We define $\Xi_{\mathtt{ECREC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover). See Appendix \ref{app:signing} for the definition of the function $\mathtt{ECDSARECOVER}$. We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required. In the case of an invalid signature ($\mathtt{ECDSARECOVER}(h, v, r, s) = \varnothing$), we return no output.

\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
\lVert \mathbf{o} \rVert &=& \begin{cases} 0 & \text{if} \quad \mathtt{ECDSARECOVER}(h, v, r, s) = \varnothing\\ 32 & \text{otherwise} \end{cases}\\
\text{if} \quad \lVert \mathbf{o} \rVert = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{KEC}\big(\mathtt{ECDSARECOVER}(h, v, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(\lVert \hyperlink{I__d}{I_{\mathbf{d}}} \rVert-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[\lVert I_{\mathbf{d}} \rVert..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}

>>>>

We define $\Xi_{\mathtt{ECREC}}$ as a precompiled contract for the elliptic curve digital signature algorithm (ECDSA) public key recovery function (ecrecover).
See Appendix \ref{app:signing} for the definition of the function $\mathtt{ECDSARECOVER}$ and the constant $\mathtt{secp256k1n}$.
We also define $\mathbf{d}$ to be the input data, well-defined for an infinite length by appending zeroes as required.
In the case of an invalid signature, we return no output.

\begin{eqnarray}
\Xi_{\mathtt{ECREC}} &\equiv& \Xi_{\mathtt{PRE}} \quad \text{where:} \\
g_{\mathrm{r}} &=& 3000\\
\lVert \mathbf{o} \rVert &=& \begin{cases}
  0 & \text{if} \quad v \notin \{27, 28\} \,\vee\, r = 0 \,\vee\, r \ge \mathtt{secp256k1n} \,\vee\, s = 0 \,\vee\, s \ge \mathtt{secp256k1n} \\
  0 & \text{if} \quad \mathtt{ECDSARECOVER}(h, v - 27, r, s) = \varnothing\\
  32 & \text{otherwise}
\end{cases}\\
\text{if} \quad \lVert \mathbf{o} \rVert = 32: &&\\
\mathbf{o}[0..11] &=& 0 \\
\mathbf{o}[12..31] &=& \mathtt{KEC}\big(\mathtt{ECDSARECOVER}(h, v - 27, r, s)\big)[12..31] \quad \text{where:}\\
\mathbf{d}[0..(\lVert \hyperlink{I__d}{I_{\mathbf{d}}} \rVert-1)] &=& I_{\mathbf{d}}\\
\mathbf{d}[\lVert I_{\mathbf{d}} \rVert..] &=& (0, 0, ...) \\
h &=& \mathbf{d}[0..31]\\
v &=& \mathbf{d}[32..63]\\
r &=& \mathbf{d}[64..95]\\
s &=& \mathbf{d}[96..127]
\end{eqnarray}
